%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full-stack developer} % Job title
    {Incedo services GmbH} % Organization
    {Stuttgart, Germany} % Location
    {Sep. 2021 - Present} % Date(s)
    {
      During my tenure at Incdeo, I made significant contributions to multiple projects, actively supported the company's
      expansion by referring highly skilled individuals to join our workforce, and played a crucial role in fostering strong
      client relationships.
      \vspace{5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          \textit{Jan. 2022 - present : }\textbf{Advanced data processing} (client : \textbf{Infineon Technologies AG}) \textit{(Productivity tool)}:
          \newline The platform aims to enhance the productivity of engineers by consolidating various features into distinct tools, such as conducting tests on semiconductor and computer chips, visualizing test results, and organizing them based on user input, as well as generating comprehensive reports from generated graphs and tables. This platform serves as a unified hub for these functionalities.
          \vspace{5mm}
        \begin{cvitems}
          \item {Maintained and developed new features for the existing application (developed using Vanilla.js).}
          \item {Reconstructed the application into a desktop application while incorporating new features using Electron.js and React.js.}
          \item {Documented the project through the use of Typedoc, MermaidJS,Storybook, JSDOC, Markdown, and README files.}
          \item {Developed automated tests with the use of Playwright (e2e tests) and Jest (snapshot , integration and unit tests).}
          \item {Set up SonarQube for code quality analysis and integration into the CI/CD pipeline.}
          \item {Established a CI/CD pipeline for the project, utilizing Artifactory, Docker, Bitbucket and Jenkins.}
          \item {Leaded a small team of developers (mostly interns) and providing them guidance and support.As well as conducting code reviews and providing feedback.}
        \end{cvitems}
        \vspace{5mm}
        \textbf{\textit{Technologies :}} Javascript/Typescript, Electron.js, React.js, Redux(RTK), Material-UI, Storybook, JSDOC, Markdown, Docker, Git, Bitbucket, Jenkins, Artifactory, Playwright, Jest, Bash scripts, Jira, Powershell scripts, SQLite, drizzle-orm, Typedoc, MermaidJs.
        \vspace{5mm}
        }
        \item {
          \textit{Sep. 2021 - Jan. 2022 : }\textbf{Incedo Lead Generator} \textit{(Internal project)} \textit{(Automation tool)}:
          \newline The objective entails the comprehensive automation of the lead generation process, encompassing activities ranging from initial outreach to subsequent follow-up messages on the LinkedIn platform and through email communication. This automation would involve the systematic retrieval of pertinent lead data, its subsequent storage, and the ability to export such data as needed. Furthermore, seamless integration with various Customer Relationship Management (CRM) tools would be a crucial aspect of this undertaking.
        \vspace{5mm}
      \begin{cvitems}
        \item {Implemented a complete overhaul of the application's front-end utilizing React.js and AntD.}
        \item {Refactored the majority of the backend code (Nest.js) to enhance performance and maintainability by implementing design patterns.}
        \item {Designed and executed the front-end using React and AntD.}
        \item {Introduced automated testing to the project using Jest.}
        \item {Set up and configured documentation frameworks including React-Styleguidist and Nest-Compodoc.}
      \end{cvitems}
      \vspace{5mm}
      \textbf{\textit{Technologies :}} Javascript/Typescript, Nestjs, React.js, AntD, sequelize, Styleguidist , JSDoc, Markdown, Docker, Git, GitLab, GitLab CI, Playwright, Jest, Asana, PostgreSQL.
      \vspace{5mm}}
       \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack developer intern} % Job title
    {ABSHORE} % Organization
    {Tunis, Tunisia} % Location
    {Mar. 2021 - Jun. 2021} % Date(s)
    {
      During my tenure as a web developer at ABSHORE, I had the opportunity to contribute to the development of a web application for a non-profit organization (\textbf{Womenvai}). The primary goal of this project was to provide the organization's members and followers with an interactive platform for event reservation and engagement with the organization's posts.
    \vspace{5mm}
    \begin{cvitems}
      \item{Collaborated with the team to create comprehensive UML diagrams, ensuring a shared understanding of the application's structure .}
      \item{Configured Drupal 8 to meet the project's specific needs, including user roles, permissions, content types, and module integration.}
      \item{Developed user-friendly interfaces using React.js, enabling event reservation and enhancing engagement with organization posts.}
      \item {Containerized the web application using Docker for streamlined deployment and management across different environments.}
    \end{cvitems}
    \vspace{5mm}
      \textbf{\textit{Technologies :}} Javascript, React.js, Drupal 8, Docker, MySQL, Apache, Git, Postman, Adobe XD.
    \vspace{5mm}
      }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Web Platform for Manual Jobs Posts (Freelance)} % Organization
    {Bizerte, Tunisia} % Location
    {Jun. 2020 - Aug. 2020} % Date(s)
    {
      Developed the front-end of a dynamic web platform catering to the manual labor industry, providing a user-friendly solution for job posting and worker discovery. Implemented intuitive user interfaces and leveraged geolocation technology to enable employers to find the closest and available workers in their vicinity.
     \vspace{5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and wireframed the web application using Adobe XD, ensuring a visually appealing and intuitive user interface.}
        \item {Developed responsive and interactive features, such as job posting forms, search functionality, and worker availability tracking.}
        \item {Translated design concepts into code by implementing the frontend using Angular.js.}
      \end{cvitems}
      \vspace{5mm}
      \textbf{\textit{Technologies :}} Javascript, Angular.js, Adobe XD, Git, Postman.
      \vspace{5mm}
    }

%---------------------------------------------------------
  \cventry
    {Game developer} % Job title
    {"SNAKE" replication (Personal project)} % Organization
    {Kebili, Tunisia} % Location
    {Jul. 2019 - Aug. 2019} % Date(s)
    {
      Aiming to put my Java skills to the test, I took on the challenge of replicating the classic game Snake using the Java programming language. Combining my passion for programming and love for games, I successfully developed a fully functional and captivating version of the game.
      \vspace{5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented the game's logic and mechanics using Java.}
        \item {Developed the game's graphical user interface using Java Swing.}
        \item {Implemented the game's audio features using the Java Sound API.}
       \end{cvitems}
       \vspace{5mm}
      \textbf{\textit{Technologies :}} Java, Java Swing, Java Sound API, Git.
      \vspace{5mm}
    }

%---------------------------------------------------------

\end{cventries}
