%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}



\begin{cvskills}
  \multicolumn{2}{l}{\textbullet\ Languages :}  \\
  \cvskill
    {Arabic}
    {Native.}
  \cvskill
    {English}
    {Professional working proficiency.}
  \cvskill
    {French}
    {Limited working proficiency.}
%  \cvskill
%    {German}
%    {Basic.}


\multicolumn{2}{l}{\textbullet\ Development methodologies :}  \\

  \cvskill
    {Agile}
    {Scrum, Kanban}
  \cvskill
    {DevOps}
    {CI/CD.}
  \cvskill
    {Software Development}
    {TDD, BDD, DDD, CDD.}

\multicolumn{2}{l}{\textbullet\ Software :}  \\

  \cvskill
    {Programming languages}
    {Node.js, Java, C , C++.}
  \cvskill
    {Scripting languages}
    {JavaScript, Groovy, PHP, Shell-script, Typescript.}
  \cvskill
    {Scheme languages}
    {JSON, XML, HTML, CSS/SCSS/SASS, LaTeX, markdown, YAML.}
  \cvskill
    {Web Server}
    {nginx (uWSGI, FastCGI), apache2 (mod\_python, mod\_php).}
  \cvskill
    {Front-end frameworks \& libs}
    {React.js, Vue.js, Three.js, Drupal 8, Bootstrap, Redux, MUI, tailwind, Angular.js , AntD.}
  \cvskill
    {Back-end frameworks \& libs}
    {Node.js, Express.js, Nest.js, Symfony.}
  \cvskill
    {Other frameworks}
    {Android (Java), Drupal 8 ,Electron.js, Next.js, Sequelize.}
  \cvskill
    {Test \& document frameworks}
    {Jest, Playwright, Puppeteer, Storybook.js, React styleGuidist.}
\multicolumn{2}{l}{\textbullet\ IDE \& Tools :}  \\

    \cvskill
      {IDEs}
      {Neovim, Eclipse, MS Visual Studio Code, JetBrains WebStorm, Android Studio.}
    \cvskill
      {Revision Control System}
      {GIT.}
    \cvskill
      {Requirements management}
      {JIRA, GitLab, GitHub, bitbucket.}
    \cvskill
      {DevOps}
      {Jenkins, Docker, Docker-compose, Github Actions, GitHub Pages, Artifactory , Gitlab CI/CD , Azure
       \newline pipelines.}
    \cvskill
      {Graphic design}
      {Basic knowledge about Adobe Products (Photoshop, XD , after effect ,Illustrator), figma.}
    \cvskill
      {Cache-Engines}
      {Redis.}
    \cvskill
      {Other}
      {Postman.}

\multicolumn{2}{l}{\textbullet\ Databases : }  \\

    \cvskill
        {SQL}
        {SQLite, MySQL, PostgreSQL, Oracle Database XE 11g.}
    \cvskill
        {non-SQL.}
        {MongoDB.}

\multicolumn{2}{l}{\textbullet\ Operating Systems :}  \\

    \cvskill
        {Linux}
        {Ubuntu, Debian, CentOS, RHEL 7, RHEL 8 .}
    \cvskill
        {Windows}
        {Windows XP, Windows 7, Windows 10, Windows 11.}
    \cvskill
        {Other}
        {MacOS.}

\multicolumn{2}{l}{\textbullet\ Branches :}  \\

\multicolumn{2}{p{\textwidth}}{\begin{cvparagraph}
Invoicing, Scraping \& browser automation , APIs, SPA (Single page applications)
SSR(server side rendering), microservice architectures, monolithic
 architectures, server management.
\end{cvparagraph} }  \\

\multicolumn{2}{l}{\textbullet\ Soft \& hard skills :}  \\

\multicolumn{2}{p{\textwidth}}{\begin{cvparagraph}
Strong analytical \& solution-oriented mindset,
Strong teamwork \& communication skills in an agile working environment ,
High degree of independence \& ability to work under pressure.
\end{cvparagraph} }  \\

\end{cvskills}
